Income and Food Price Transmission\footnote{Revised version of MS 2015310 ``Income and Price Transmission''. Submitted to \emph{Agricultural Economics} for 2. round review. I thank two anonymous reviewers for their valuable comments.}

### 2016-03-02 tables.Rnw
Revised table script for 2. round revision version of paper

% !Rnw root = Master.Rnw

\SweaveInput{regressions.Rnw}

\section{Tables}

<<echo=FALSE, results=tex>>=
library(stargazer)
sumdat = merge(infl, icp_data[,-5], by = "iso3c", all.x=TRUE)
sumdat = merge(sumdat, staples, by = "iso3c", all.x=TRUE)
sumdat = merge(sumdat, cdep, by = "iso3c", all.x=TRUE)
colnames(sumdat)=c("iso", "FPI inflation 07-08", "CPI inflation 07-08", "Real FPI growth 07-08", "FPI inflation 10-11", "CPI inflation 10-11", "Real FPI growth 10-11", "GDP", "cons", "food", "cshare", "cdep")

stargazer(sumdat, digits=1, title='Summary statistics', label = "tab:sumstat", 
          notes=c("Notes: 07-08 and 10-11 refer to the periods 2007:1-2008:6 and 2010:1-2010:12,", 
                  "respectively. `GDP, `cons' and `food' refer to per capita income, -consumption",
                  "and -food expenditure respectively in the year 2005. `cshare' refers to a coun-",
                  "try's percentage dietary energy supply derived from cereals, roots and tubers.", 
                  "`cdep' refers to a country's cereal import dependency ratio, both with respect",
                  "to the years 2004-06. Source: ILO, World Bank, FAO. Own calculations"),
          notes.append=FALSE,
          notes.align="l")
@

<<results=tex,echo=F>>=
<<dom_infl_0708>>
stargazer(m1, m2, m3, m4, m5, m6, title='Income related determinants of domestic food price changes 2007:1-2008:6', label = "tab:2007-8-regressions", dep.var.labels=c("FPI inflation","Real FPI growth"), no.space=TRUE, se = list(rse1, rse2, rse3, rse4, rse5, rse6), omit.stat = c("adj.rsq","f", "ser"), font.size = "footnotesize", covariate.labels=c("$log(GDP)$", "$log(GDP)^2$", "$log(cons)$", "$log(cons)^2$", "$log(food)$", "$log(food)^2$", "$cshare$", "$cdep$", "$cshare \\times cdep$"), 
          notes=c("Robust standard errors are reported in parentheses underneath the coefficients.",
                  "Significance at p = 0.1, p = 0.05 and p = 0.01 are denoted by `*', `**' and `***'", 
                  "respectively"),
          notes.append=FALSE,
          notes.align="l",
          notes.label="Notes:")
@

<<results=tex,echo=F>>=
<<dom_infl_1011>>
stargazer(m1, m2, m3, m4, m5, m6, title='Income related determinants of domestic food price changes 2010:1-2010:12', label = "tab:2010-11-regressions", dep.var.labels=c("FPI inflation","Real FPI growth"), no.space=TRUE, se = list(rse1, rse2, rse3, rse4, rse5, rse6), omit.stat = c("adj.rsq","f", "ser"), font.size = "footnotesize", covariate.labels=c("$log(GDP)$", "$log(GDP)^2$", "$log(cons)$", "$log(cons)^2$", "$log(food)$", "$log(food)^2$", "$cshare$", "$cdep$", "$cshare \\times cdep$"), 
          notes=c("Robust standard errors are reported in parentheses underneath the coefficients.",
                  "Significance at p = 0.1, p = 0.05 and p = 0.01 are denoted by `*', `**' and `***'", 
                  "respectively"),
          notes.append=FALSE,
          notes.align="l",
          notes.label="Notes:")
@

<<results=tex, echo=FALSE>>=
<<ts_pt>>
stargazer(m1, m2, m3, m4, m5, m6, title='Long run multiplier (LRM) regressions', label = "tab:lri-regressions", dep.var.labels=c("LRM, FPI inflation","LRM, real FPI growth"), no.space=TRUE, se = list(rse1, rse2, rse3, rse4, rse5, rse6), omit.stat = c("adj.rsq","f", "ser"), font.size = "footnotesize", covariate.labels=c("$log(GDP)$", "$log(GDP)^2$", "$log(cons)$", "$log(cons)^2$", "$log(food)$", "$log(food)^2$", "$cshare$", "$cdep$", "$cshare \\times cdep$"),
          notes=c("Robust standard errors are reported in parentheses underneath the coefficients.",
                  "Significance at p = 0.1, p = 0.05 and p = 0.01 are denoted by `*', `**' and `***'", 
                  "respectively"),
          notes.append=FALSE,
          notes.align="l",
          notes.label="Notes:")
@

<<results=tex, echo=FALSE>>=
<<panel_pt>>
stargazer(m1, m2, m3, m4, m5, m6, 
          title='Panel regressions', 
          label = "tab:panel-regressions", 
          font.size = "footnotesize", 
          no.space=TRUE, 
          se = list(rse1, rse2, rse3, rse4, rse5, rse6), 
          omit.stat = c("adj.rsq","f"), 
          dep.var.labels=c("$\\Delta log(FPI_{t})$","$\\Delta log(rFPI_{t})$"), 
          omit = 1:12, 
          covariate.labels=c("$\\Delta log(FAO_{t-6})$", "$\\Delta log(FAO_{t-6}) \\times log(GDP)$","$\\Delta log(FAO_{t-6}) \\times log(GDP)^2$", "$\\Delta log(FAO_{t-6}) \\times log(cons)$", "$\\Delta log(FAO_{t-6}) \\times log(cons)^2$", "$\\Delta log(FAO_{t-6}) \\times log(food)$", "$\\Delta log(FAO_{t-6}) \\times log(food)^2$"), 
          notes=c("Robust standard errors are reported in parentheses underneath the coef-",
                  "ficients. Significance at p = 0.1, p = 0.05 and p = 0.01 are denoted by `*',", 
                  " `**' and `***' respectively"),
          notes.append=FALSE,
          notes.align="l",
          notes.label="Notes:")
@

<<tpmat, echo=FALSE>>=
tp = matrix(NA, nrow=6, ncol=4)

<<dom_infl_0708>>
tp[1,1] = -m1$coefficients[2]/(2*m1$coefficients[3])
tp[2,1] = -m2$coefficients[2]/(2*m2$coefficients[3])
tp[3,1] = -m3$coefficients[2]/(2*m3$coefficients[3])
tp[4,1] = -m4$coefficients[2]/(2*m4$coefficients[3])
tp[5,1] = -m5$coefficients[2]/(2*m5$coefficients[3])
tp[6,1] = -m6$coefficients[2]/(2*m6$coefficients[3])

<<dom_infl_1011>>
tp[1,2] = -m1$coefficients[2]/(2*m1$coefficients[3])
tp[2,2] = -m2$coefficients[2]/(2*m2$coefficients[3])
tp[3,2] = -m3$coefficients[2]/(2*m3$coefficients[3])
tp[4,2] = -m4$coefficients[2]/(2*m4$coefficients[3])
tp[5,2] = -m5$coefficients[2]/(2*m5$coefficients[3])
tp[6,2] = -m6$coefficients[2]/(2*m6$coefficients[3])

<<ts_pt>>
tp[1,3] = -m1$coefficients[2]/(2*m1$coefficients[3])
tp[2,3] = -m2$coefficients[2]/(2*m2$coefficients[3])
tp[3,3] = -m3$coefficients[2]/(2*m3$coefficients[3])
tp[4,3] = -m4$coefficients[2]/(2*m4$coefficients[3])
tp[5,3] = -m5$coefficients[2]/(2*m5$coefficients[3])
tp[6,3] = -m6$coefficients[2]/(2*m6$coefficients[3])

<<panel_pt>>
tp[1,4] = -m1$coefficients[8]/(2*m1$coefficients[9])
tp[2,4] = -m2$coefficients[8]/(2*m2$coefficients[9])
tp[3,4] = -m3$coefficients[8]/(2*m3$coefficients[9])
tp[4,4] = -m4$coefficients[8]/(2*m4$coefficients[9])
tp[5,4] = -m5$coefficients[8]/(2*m5$coefficients[9])
tp[6,4] = -m6$coefficients[8]/(2*m6$coefficients[9])

tp = exp(tp)
@

\begin{table}
\caption{Estimated turning points}
\label{tab:tp}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
Model & dep. var & indep. var & tp (\$, PPP) & significance & \# of countries\tabularnewline
\hline 
\hline 
(\ref{eq:infl_model}) & FPI infl. 07-08  & GDP & \Sexpr{round(tp[1,1],0)} & no & \Sexpr{nrow(data_0708[which(data_0708$GDP< tp[1,1] & data_0708$GDP >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$GDP>0), ])}  (\Sexpr{round(nrow(data_0708[which(data_0708$GDP< tp[1,1] & data_0708$GDP >0), ])/nrow(data_0708[which(data_0708$GDP>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:infl_model}) & FPI infl. 07-08 & cons & \Sexpr{round(tp[2,1],0)} & no & \Sexpr{nrow(data_0708[which(data_0708$cons< tp[2,1] & data_0708$cons >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$cons>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$cons< tp[2,1] & data_0708$cons >0), ])/nrow(data_0708[which(data_0708$cons>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:infl_model}) & FPI infl. 07-08 & food & \Sexpr{round(tp[3,1],0)}  & yes & \Sexpr{nrow(data_0708[which(data_0708$food< tp[3,1] & data_0708$food >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$food>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$food< tp[3,1] & data_0708$food >0), ])/nrow(data_0708[which(data_0708$food>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:infl_model}) & rFPI gr. 07-08 & GDP & \Sexpr{round(tp[4,1],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$GDP< tp[4,1] & data_0708$GDP >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$GDP>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$GDP< tp[4,1] & data_0708$GDP >0), ])/nrow(data_0708[which(data_0708$GDP>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:infl_model}) & rFPI gr. 07-08 & cons & \Sexpr{round(tp[5,1],0)}  & yes & \Sexpr{nrow(data_0708[which(data_0708$cons< tp[5,1] & data_0708$cons >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$cons>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$cons< tp[5,1] & data_0708$cons >0), ])/nrow(data_0708[which(data_0708$cons>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:infl_model}) & rFPI gr. 07-08 & food & \Sexpr{round(tp[6,1],0)}  & yes & \Sexpr{nrow(data_0708[which(data_0708$food< tp[6,1] & data_0708$food >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$food>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$food< tp[6,1] & data_0708$food >0), ])/nrow(data_0708[which(data_0708$food>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:infl_model}) & FPI infl. 10-11 & GDP & \Sexpr{round(tp[1,2],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$GDP< tp[1,2] & data_0708$GDP >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$GDP>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$GDP< tp[1,2] & data_0708$GDP >0), ])/nrow(data_0708[which(data_0708$GDP>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:infl_model}) & FPI infl. 10-11 & cons & \Sexpr{round(tp[2,2],0)} & no &  \Sexpr{nrow(data_0708[which(data_0708$cons< tp[2,2] & data_0708$cons >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$cons>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$cons< tp[2,2] & data_0708$cons >0), ])/nrow(data_0708[which(data_0708$cons>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:infl_model}) & FPI infl. 10-11 & food & \Sexpr{round(tp[3,2],0)} & yes &  \Sexpr{nrow(data_0708[which(data_0708$food< tp[3,2] & data_0708$food >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$food>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$food< tp[3,2] & data_0708$food >0), ])/nrow(data_0708[which(data_0708$food>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:infl_model}) & rFPI gr. 10-11 & GDP & \Sexpr{round(tp[4,2],0)} & yes &  \Sexpr{nrow(data_0708[which(data_0708$GDP< tp[4,2] & data_0708$GDP >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$GDP>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$GDP< tp[4,2] & data_0708$GDP >0), ])/nrow(data_0708[which(data_0708$GDP>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:infl_model}) & rFPI gr. 10-11 & cons & \Sexpr{round(tp[5,2],0)} & yes &  \Sexpr{nrow(data_0708[which(data_0708$cons< tp[5,2] & data_0708$cons >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$cons>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$cons< tp[5,2] & data_0708$cons >0), ])/nrow(data_0708[which(data_0708$cons>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:infl_model}) & rFPI gr. 10-11 & food & \Sexpr{round(tp[6,2],0)} & yes &  \Sexpr{nrow(data_0708[which(data_0708$food< tp[6,2] & data_0708$food >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$food>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$food< tp[6,2] & data_0708$food >0), ])/nrow(data_0708[which(data_0708$food>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:ptreg}) & LR multiplier & GDP & \Sexpr{round(tp[1,3],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$GDP< tp[1,3] & data_0708$GDP >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$GDP>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$GDP< tp[1,3] & data_0708$GDP >0), ])/nrow(data_0708[which(data_0708$GDP>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:ptreg}) & LR multiplier & cons & \Sexpr{round(tp[2,3],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$cons< tp[2,3] & data_0708$cons >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$cons>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$cons< tp[2,3] & data_0708$cons >0), ])/nrow(data_0708[which(data_0708$cons>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:ptreg}) & LR multiplier & food & \Sexpr{round(tp[3,3],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$food< tp[3,3] & data_0708$food >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$food>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$food< tp[3,3] & data_0708$food >0), ])/nrow(data_0708[which(data_0708$food>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:ptreg}) & LR multiplier & GDP & \Sexpr{round(tp[4,3],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$GDP< tp[4,3] & data_0708$GDP >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$GDP>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$GDP< tp[4,3] & data_0708$GDP >0), ])/nrow(data_0708[which(data_0708$GDP>0), ])*100,0)}\%)\tabularnewline
\hline
(\ref{eq:ptreg}) & LR multiplier & cons & \Sexpr{round(tp[5,3],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$cons< tp[5,3] & data_0708$cons >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$cons>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$cons< tp[5,3] & data_0708$cons >0), ])/nrow(data_0708[which(data_0708$cons>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:ptreg}) & LR multiplier & food & \Sexpr{round(tp[6,3],0)} & no & \Sexpr{nrow(data_0708[which(data_0708$food< tp[6,3] & data_0708$food >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$food>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$food< tp[6,3] & data_0708$food >0), ])/nrow(data_0708[which(data_0708$food>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:panel_model}) & mth FPI infl & GDP & \Sexpr{round(tp[1,4],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$GDP< tp[1,4] & data_0708$GDP >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$GDP>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$GDP< tp[1,4] & data_0708$GDP >0), ])/nrow(data_0708[which(data_0708$GDP>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:panel_model}) & mth FPI infl & cons & \Sexpr{round(tp[2,4],0)} & no & \Sexpr{nrow(data_0708[which(data_0708$cons< tp[2,4] & data_0708$cons >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$cons>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$cons< tp[2,4] & data_0708$cons >0), ])/nrow(data_0708[which(data_0708$cons>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:panel_model}) & mth FPI infl & food & \Sexpr{round(tp[3,4],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$food< tp[3,4] & data_0708$food >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$food>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$food< tp[3,4] & data_0708$food >0), ])/nrow(data_0708[which(data_0708$food>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:panel_model}) & mth rFPI gr. & GDP & \Sexpr{round(tp[4,4],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$GDP< tp[4,4] & data_0708$GDP >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$GDP>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$GDP< tp[4,4] & data_0708$GDP >0), ])/nrow(data_0708[which(data_0708$GDP>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:panel_model}) & mth rFPI gr. & cons & \Sexpr{round(tp[5,4],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$cons< tp[5,4] & data_0708$cons >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$cons>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$cons< tp[5,4] & data_0708$cons >0), ])/nrow(data_0708[which(data_0708$cons>0), ])*100,0)}\%)\tabularnewline
\hline 
(\ref{eq:panel_model}) & mth rFPI gr. & food & \Sexpr{round(tp[6,4],0)} & no & \Sexpr{nrow(data_0708[which(data_0708$food< tp[6,4] & data_0708$food >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$food>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$food< tp[6,4] & data_0708$food >0), ])/nrow(data_0708[which(data_0708$food>0), ])*100,0)}\%)\tabularnewline
\hline 
\multicolumn{6}{l}{Notes: The numbers in the fourth column refer to the estimated income or expenditure}\tabularnewline
\multicolumn{6}{l}{turning point (tp). The fifth column indicates whether the estimated quadratic term}\tabularnewline
\multicolumn{6}{l}{coefficients are individually significant at the 10 percent level. The last column shows}\tabularnewline
\multicolumn{6}{l}{the number of countries in the sample with a per capita income or expenditure levels}\tabularnewline 
\multicolumn{6}{l}{below the estimated turning point.}
\end{tabular}
\end{center}
\end {table}

>>>>

% !Rnw root = master.Rnw

\section*{Tables}

<<results=tex,echo=F>>=
library(stargazer)
reg.list = readRDS("fc_reg0708_m.rds")
se.list = readRDS("fc_reg0708_se.rds")

stargazer(reg.list[[1]], reg.list[[2]], reg.list[[3]], reg.list[[4]],
          title='Determinants of domestic food price changes 2007-8', 
          label = "tab:07-08-fc-regressions", 
          dep.var.labels=c("FPI inflation", "RFPI growth"),
          no.space=TRUE,
          se = list(se.list[[1]], se.list[[2]], se.list[[3]], se.list[[4]]), 
          keep.stat = c("rsq", "n", "aic"),
          font.size = "small", 
          covariate.labels=c("$\\Delta ER$",
                             "$GDP$",
                             "$GDP^{2}$", 
                             "$CCONS$", 
                             "$CIMP$", 
                             "$CEXP$",
                             "$LLDC$", 
                             "$STE$",
                             "$TO$", 
                             "$DTF$", 
                             "$LPI$"),
          notes=c("*, ** and *** signify significance at the 10, 5 and 1 percent",
                  "levels, respectively. Robust standard errors in parentheses;", 
                  "samples exclude outliers defined as observations $\\pm$ 3.5 stan-", 
                  "dard deviations from the mean of the dependent variable.", 
                  "A description of the variables and their sources can be found", 
                  "in table \\ref{tab:cs_data} and section \\ref{sec:analysis}."),
          notes.append=FALSE,
          notes.align="l")
@

<<results=tex,echo=F>>=
library(stargazer)
reg.list = readRDS("fpi_pt_reg_m.rds")
se.list = readRDS("fpi_pt_reg_se.rds")
bp.stat.list = readRDS("fpi_bptest_stat.rds")
bp.p.list = readRDS("fpi_bptest_p.rds")

stargazer(reg.list[[1]], reg.list[[2]], reg.list[[3]], reg.list[[4]],
          title='Determinants of long run FPI transmission rates', 
          label = "tab:fpi-pt-regressions", 
          dep.var.labels=c("FPI LRM (6 lags)"), 
          column.labels = c("OLS", "WLS"),
          column.separate = c(2, 2),
          no.space=TRUE,
          se = list(se.list[[1]], se.list[[2]], se.list[[3]], se.list[[4]]), 
          omit.stat = c("adj.rsq","f", "ser"), 
          font.size = "small", 
          covariate.labels=c("$GDP$",
                             "$GDP^{2}$", 
                             "$CCONS$", 
                             "$CIMP$", 
                             "$CEXP$",
                             "$LLDC$", 
                             "$STE$",
                             "$TO$", 
                             "$DTF$", 
                             "$LPI$"),
          notes=c("*, ** and *** signify significance at the 10, 5 and 1 percent",
                  "levels, respectively. Robust standard errors in parentheses;", 
                  "samples exclude outliers defined as observations $\\pm$ 3.5 stan-", 
                  "dard deviations from the mean of the dependent variable.", 
                  "A description of the variables and their sources can be found", 
                  "in table \\ref{tab:cs_data} and section \\ref{sec:analysis}."),
          notes.append=FALSE,
          notes.align="l")
@

<<results=tex, echo=FALSE>>=
library(plm)
reg.list = readRDS("panel_reg_m.rds")
se.list = readRDS("panel_reg_se.rds")

stargazer(reg.list[[1]], reg.list[[3]],
          title='Determinants of short run FPI transmission rates', 
          label = "tab:panel-regressions", 
          dep.var.labels=c("FPI inflation", "RFPI growth"),
          single.row = TRUE,
          se = list(se.list[[1]], se.list[[3]]),
          omit = c("adj.fpi", "rfpi"),
          omit.stat = c("adj.rsq","f", "ser"), 
          font.size = "small",
          covariate.labels=c("$\\pi_{t}^{i}$",
                             "$\\pi_{t-1}^{i}$",
                             "$\\Delta ER_{t}$",
                             "$\\Delta ER_{t-1}$",
                             "$\\pi_{t-1}^{i}\\times GDP$",
                             "$\\pi_{t-1}^{i}\\times GDP^2$", 
                             "$\\pi_{t-1}^{i}\\times CCONS$", 
                             "$\\pi_{t-1}^{i}\\times CIMP$", 
                             "$\\pi_{t-1}^{i}\\times CEXP$",
                             "$\\pi_{t-1}^{i}\\times LLDC$", 
                             "$\\pi_{t-1}^{i}\\times STE$", 
                             "$\\pi_{t-1}^{i}\\times TO$", 
                             "$\\pi_{t-1}^{i}\\times DTF$", 
                             "$\\pi_{t-1}^{i}\\times LPI$"),
          notes=c("*, ** and *** signify significance at the 10, 5 and 1",
                  "percent levels, respectively. Robust clustered standard", 
                  "errors in parentheses. A description of the variables and", 
                  "their sources can be found in table \\ref{tab:cs_data} and section \\ref{sec:analysis}."),
          notes.append=FALSE,
          notes.align="l")
@

<<echo=FALSE>>=
load("infl_ctr_dat_0708.Rda")
dat = ctr.dat.0708
r1 = readRDS("fc_reg0708_m.rds")
r2 = readRDS("fpi_pt_reg_m.rds")
r3 = readRDS("panel_reg_m.rds")

tp = matrix(NA, nrow=6, ncol=1)
tp[1,1] = -coef(r1[[1]])["log(gdp.const.int)"]/(2*coef(r1[[1]])["I(log(gdp.const.int)^2)"])
tp[2,1] = -coef(r1[[3]])["log(gdp.const.int)"]/(2*coef(r1[[3]])["I(log(gdp.const.int)^2)"])
tp[3,1] = -coef(r2[[1]])["log(gdp.const.int)"]/(2*coef(r2[[1]])["I(log(gdp.const.int)^2)"])
tp[4,1] = -coef(r2[[3]])["log(gdp.const.int)"]/(2*coef(r2[[3]])["I(log(gdp.const.int)^2)"])
tp[5,1] = -coef(r3[[1]])["I(lag(diff(log(fao.fpi)), 1) * log(gdp.const.int))"]/
  (2*coef(r3[[1]])["I(lag(diff(log(fao.fpi)), 1) * I(log(gdp.const.int)^2))"])
tp[6,1] = -coef(r3[[3]])["I(lag(diff(log(fao.fpi)), 1) * log(gdp.const.int))"]/
  (2*coef(r3[[3]])["I(lag(diff(log(fao.fpi)), 1) * I(log(gdp.const.int)^2))"])

tp = exp(tp)
n.gdp = length(which(!is.na(dat$gdp.const.int)))

nc = matrix(NA, nrow=6, ncol=1)
nc[1,1] = nrow(dat[which(dat$gdp.const.int< tp[1,1] & !is.na(dat$gdp.const.int)), ])
nc[2,1] = nrow(dat[which(dat$gdp.const.int< tp[2,1] & !is.na(dat$gdp.const.int)), ])
nc[3,1] = nrow(dat[which(dat$gdp.const.int< tp[3,1] & !is.na(dat$gdp.const.int)), ])
nc[4,1] = nrow(dat[which(dat$gdp.const.int< tp[4,1] & !is.na(dat$gdp.const.int)), ])
nc[5,1] = nrow(dat[which(dat$gdp.const.int< tp[5,1] & !is.na(dat$gdp.const.int)), ])
nc[6,1] = nrow(dat[which(dat$gdp.const.int< tp[6,1] & !is.na(dat$gdp.const.int)), ])

nc.pc.mean =  matrix(NA, nrow=3, ncol=1)
nc.pc.mean[1] = mean(nc[1:5])/n.gdp
nc.pc.mean[2] = mean(nc[5])/n.gdp
nc.pc.mean[3] = mean(nc[1:4])/n.gdp
nc.pc.mean = nc.pc.mean*100

tp.mean =  matrix(NA, nrow=3, ncol=1)
tp.mean[1] = mean(tp[1:5])
tp.mean[2] = mean(tp[5])
tp.mean[3] = mean(tp[1:4])
save(nc.pc.mean, file = "tp_ctr_mean.Rda")
save(tp.mean, file = "tp_ctr_mean1.Rda")
@

\begin{table}
\centering
\begin{threeparttable}
\caption{Estimated turning points (TPs)}
\label{tab:tp}
\small
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
Table & Estimator & Dependent variable & TP (\$, PPP) & Left of TP\tabularnewline
\hline 
\hline
\ref{tab:07-08-fc-regressions} & OLS & FPI infl. 07-08  &  \Sexpr{round(tp[1,1],0)} & \Sexpr{nc[1,1]}/\Sexpr{n.gdp} \tabularnewline
\hline 
\ref{tab:07-08-fc-regressions} & OLS & RFPI growth 07-08  &  \Sexpr{round(tp[2,1],0)} & \Sexpr{nc[2,1]}/\Sexpr{n.gdp} \tabularnewline
\hline 
\ref{tab:fpi-pt-regressions} & OLS & FPI LRM  &  \Sexpr{round(tp[3,1],0)} & \Sexpr{nc[3,1]}/\Sexpr{n.gdp} \tabularnewline
\hline 
\ref{tab:fpi-pt-regressions} & WLS & FPI LRM  &  \Sexpr{round(tp[4,1],0)} & \Sexpr{nc[4,1]}/\Sexpr{n.gdp} \tabularnewline
\hline 
\ref{tab:panel-regressions} & FE & $\Delta \log(FPI)_{t}$  &  \Sexpr{round(tp[5,1],0)} & \Sexpr{nc[5,1]}/\Sexpr{n.gdp} \tabularnewline
\hline
\end{tabular}
\begin{tablenotes}
\item \emph{Note:} The numbers in the fourth column are the estimated turning points based on coefficients from the regression specified in the first three columns. I.e. the per capita income level corresponding to the highest level of predicted domestic food inflation or price transmission. The final column calculates how many countries that have per capita income less than the level corresponding to the estimated  turning point, relative to the total number of countries in the sample with data on income. 
\end{tablenotes}
\end{threeparttable}
\end{table}
